---
title: "BIOL 432 - Assignment 1"
author: "David Griffin"
date: '2023-01-11'
output: html_document
---
    
[Link to my repository](https://github.com/davidgriffin124/BIOL432_Assignment1)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<br>

##### Loading Library
```{r}
library(dplyr)
library(ggplot2)
```
<br>

##### Script generating limb data for 5 species of capuchin monkey
```{r}
source('dataGenerato.R')
```
<br>

##### Script estimating limb volume and adding column
```{r}
source('volumeEstimato.R')
```
<br>

##### Loading revised limb data
```{r}
limbdat = read.csv("measurements.csv")
```
<br>

##### Sorting data by Species, then b Observer, then by Limb Volume
```{r}
limbdat = limbdat %>%
  arrange(Organism, Observer, Limb_volume)
```
<br>

##### Table displaying average Limb Volume by Species
```{r}
limbdat %>%
  group_by(Organism)%>%
  summarize(Average_Limb_Volume = mean(Limb_volume))
```
<br>

##### Table displaying number of observations by Species x Observer
```{r}
limbdat %>%
  group_by(Organism, Observer) %>%
  count()
```
<br>

##### Box plot comparing species limb volume
```{r}
ggplot(limbdat, aes(x=Organism, y=Limb_volume)) + geom_boxplot() + xlab("\n Species") + ylab("Limb Volume \n") + theme_bw() + labs(title = "Limb Volume Frequency for Capuchin Monkeys", caption = "\n\n Figure 1. Limb volume distributions for 100 random samples of 5 species of capuchin monkey") + theme(plot.title = element_text(hjust = 0.5), plot.caption = element_text(hjust = 0.5))
```

<br>

##### Multi-panel plot showing frequency histograms for each species
```{r}
ggplot(data = limbdat, aes(x = Limb_volume)) + geom_histogram() + xlab("\n Limb Volume") + ylab("Count \n") + facet_wrap(~Organism, nrow = 2, ncol = 3) + theme_bw() + labs(title = "Limb Volume Frequency for Capuchin Monkeys", caption = "\n\n Figure 2. Frequency of various limb volumes for 100 random samples of 5 species of capuchin monkey") + theme(plot.title = element_text(hjust = 0.5), plot.caption = element_text(hjust = 0.5))
```

